---
title: "Associations Between a Transdiagnostic Core Vulnerability and Internalizing Symptoms: A Network Analysis"
subtitle: "Supplementary Material"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<!-- # loading packages -->

```{r}
library(tidyverse)
library(bootnet)
library(kableExtra)
library(haven)
library(psych)
library(qgraph)
library(psychonetrics)
library(lavaan)
library(networktools)
```

<!-- # loading data labels -->

```{r}
variables <- as.data.frame(readxl::read_xlsx("../data/variablebook.xlsx")) %>% 
  select("label", "variablename", "variable_description_short", "variable_description_clean")
```

\newpage

# Appendix 1: Preliminary fitting of 57-node network model

<!-- # loading data -->

```{r}
networkdata_allitems_sg <- read.csv("../data/exploratory/networkdata_allitems_sg.csv")
```

## Estimated network
Please see table in next section for a description of each node label.

```{r}
# defining node labels for graph
nodelabels_57 <- data.frame(variablename = colnames(networkdata_allitems_sg)) %>% 
  left_join(variables, by = "variablename") %>%
  select(label)

#estimating network
network_57 <- estimateNetwork(networkdata_allitems_sg,
                             default = "EBICglasso",
                             corMethod = "spearman",
                             labels = nodelabels_57$label,
                             missing = "pairwise",
                             sampleSize = "pairwise_average",
                             tuning = 0.5)

# custom function for defining legend vectors
# DO NOT use if there is only one element
# var_start argument should be argument for dplyr::starts_with
def_legend <- function(data, var_start){
  
  data %>% 
    select(starts_with(var_start)) %>% 
    colnames() %>%  
    match(colnames(data))
}

# defining grouping for legend
group_subscale_57 <- list("GAD" = def_legend(networkdata_allitems_sg,"gad"),
                       "PHQ-9" = def_legend(networkdata_allitems_sg,"phq"),
                       "SMPD" = def_legend(networkdata_allitems_sg,"smpd"),
                       "SMSAD" = def_legend(networkdata_allitems_sg,"smsp"),
                       "DOCS" = def_legend(networkdata_allitems_sg,"docs"),
                       "TPESS" = c(which(colnames(networkdata_allitems_sg) == "tpess")))

# printing plot
plot_57 <- plot(network_57,
     groups = group_subscale_57,
     layout = "spring",
     cut = 0,
     palette = "pastel",
     vsize = 4,
     labels = nodelabels_57$label,
     label.cex = 1.35,
     border.width = 0.75,
     legend.cex = 0.5)

```

\newpage

## Summary of nodes included in the 57-node network

```{r}
data.frame(variablename = colnames(networkdata_allitems_sg)) %>% 
  left_join(variables, by = "variablename") %>% 
  select(label, variable_description_short) %>% kbl(format = "latex", col.names = c("Node Label", "Description"), caption = "Item content for 57-node network", booktabs = TRUE, longtable = TRUE)  %>%
  pack_rows("GAD-7", 1, 7) %>% 
  pack_rows("PHQ-9", 8, 16) %>% 
  pack_rows("SMPD", 17, 26) %>% 
  pack_rows("SMSAD", 27, 36) %>% 
  pack_rows("DOCS", 37, 56) %>% 
  pack_rows("TPESS", 57, 57) %>% 
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "30em") %>% 
  footnote(
    general_title = "Note.",
    general = "GAD-7 = Generalized Anxiety Disorder-7; PHQ-9 = Patient Health Questionnaire-9; SMPD = Severity Measure for Panic Disorder-Adult; SMSAD = Severity Measure for Social Anxiety Disorder-Adult; DOCS = Dimensional Obsessive-Compulsive Scale; TPESS = Transdiagnostic Processes of Emotional Symptoms Scale; Item descriptions for PHQ-9, GAD-7, and DOCS adapted from Hsu et al. (2022), Mossman et al. (2017), and Abramowitz et al. (2010) respectively.",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE)
```

\newpage

# Appendix 2: Distribution of responses to PHQ-9, GAD-7, SMPD, and SMSAD items
The size of the circles in each plot reflects the proportion of the sample that selected the corresponding item response.

<!-- # importing data-->

```{r}
networkdata_sg <- read.csv("../data/exploratory/networkdata_sg.csv")
```

## Patient Health Questionnaire-9 (PHQ-9)

```{r}
phq <- networkdata_sg[which(colnames(networkdata_sg) == "phq1"):which(colnames(networkdata_sg) == "phq9")] %>% 
  pivot_longer(names_to = "item",
               values_to = "response",
               cols = everything()) %>%
  left_join(variables, by = c("item" = "variablename"))

ggplot(phq, aes(x = response, y = variable_description_short)) +
  geom_count(aes(size = after_stat(prop)), na.rm = TRUE) +
  scale_size_area(max_size = 10) +
  labs(x = "Response", y = "Item") +
  theme_light() +
  theme(legend.position = "none", axis.title.y = element_blank())
```

## Generalized Anxiety Disorder-7 (GAD-7)

```{r}
gad <- networkdata_sg[which(colnames(networkdata_sg) == "gad1"):which(colnames(networkdata_sg) == "gad7")] %>% 
  pivot_longer(names_to = "item",
               values_to = "response",
               cols = everything()) %>%
  left_join(variables, by = c("item" = "variablename"))

ggplot(gad, aes(x = response, y = variable_description_short)) +
  geom_count(aes(size = after_stat(prop)), na.rm = TRUE) +
  scale_size_area(max_size = 10) +
  labs(x = "Response", y = "Item") +
  theme_light() +
  theme(legend.position = "none", axis.title.y = element_blank())
```

## Severity Measure for Panic Disorder-Adult (SMPD)

```{r}
smpd <- networkdata_sg[which(colnames(networkdata_sg) == "smpd1"):which(colnames(networkdata_sg) == "smpd10")] %>% 
  pivot_longer(names_to = "item",
               values_to = "response",
               cols = everything()) %>%
  left_join(variables, by = c("item" = "variablename"))

ggplot(smpd, aes(x = response, y = variable_description_short)) +
  geom_count(aes(size = after_stat(prop)), na.rm = TRUE) +
  scale_size_area(max_size = 10) +
  labs(x = "Response", y = "Item") +
  theme_light() +
  theme(legend.position = "none", axis.title.y = element_blank())
```

## Severity Measure for Social Anxiety Disorder-Adult (SMSAD)

```{r}
smsad <- networkdata_sg[which(colnames(networkdata_sg) == "smsp1"):which(colnames(networkdata_sg) == "smsp10")] %>% 
  pivot_longer(names_to = "item",
               values_to = "response",
               cols = everything()) %>%
  left_join(variables, by = c("item" = "variablename"))

ggplot(smsad, aes(x = response, y = variable_description_short)) +
  geom_count(aes(size = after_stat(prop)), na.rm = TRUE) +
  scale_size_area(max_size = 10) +
  labs(x = "Response", y = "Item") +
  theme_light() +
  theme(legend.position = "none", axis.title.y = element_blank())
```

\newpage

# Appendix 3: Robustness Analysis (Bootstrapped Confidence Intervals of Edge Weights)

Each horizontal line represents an edge in the network; lines were ordered in descending order (highest edge weight to lowest edge weight). Red dots indicate sample values and the grey areas indicate bootstrapped confidence intervals. Axis labels have been removed to avoid clutter. 

```{r}
# generating non-parametric bootstraps samples of network_sg
# bootstraps of network_sg (see analysis_expnet.R) computationally intensive to execute so output was saved to a .rds file. Data to be loaded with readRDS 
nonparboot <- readRDS(file = "../data/exploratory/rds/nonparboot.rds")
```

```{r, fig.dim = c(7, 7)}
#plotting bootstrapped CIs for edge weights
plot(nonparboot, order = "sample", labels = FALSE, areaAlpha = 0.4)
```
\newpage

# Appendix 4: Bridge Strength
We felt that it was necessary to statistically evaluate the degree to which the core vulnerability exhibits the properties of a general psychological vulnerability by examining the bridge strength – a centrality measure that indicates a given node’s total connectivity with nodes from other communities (Jones et al., 2019). We report this analysis here for the interested reader.

In the current context, there are six communities: (1) the core vulnerability, (2) depression symptoms, (3) generalized anxiety symptoms, (4) symptoms of panic disorder, (5) symptoms of social anxiety disorder, and (6) the subscales of OCD. If the core vulnerability has the properties of a general psychological vulnerability, it should possess the highest bridge strength among nodes within the network. That is, it should have the strongest connectivity to the symptoms from the five other communities in our network. If it does not and if a symptom were to have a higher bridge strength than the core vulnerability, then the notion that the core vulnerability is akin to a general psychological vulnerability will be challenged.

```{r}
# creating communities
communities <- list("gad"= c(1:7),
                    "phq9" = c(8:16),
                    "smpd" = c(17:26),
                    "smsp" = c(27:36),
                    "docs" = c(37:40),
                    "tpess" = c(41))
```

```{r, out.width = "300%"}
#loading exploratory network plot data
plot_sg <- readRDS("../data/appendix/rds/plot_sg.rds")

#computing bridge centrality
bridgecen_sg <- bridge(plot_sg,communities = communities)
```

The plot below depicts the bridge strength of each of the 41 nodes in our network. The TPESS mean score node (which represents the core vulnerability) clearly had the highest bridge strength of the nodes in the network. Importantly, the bridge strength of the core vulnerability node far surpassed the bridge strength of any symptom in the network, lending (tentative) credence to the notion that the core vulnerability (and not other specific symptoms within the network) possess the qualities of a general psychological vulnerability.

```{r}
plot_bridgecen_sg <- plot(bridgecen_sg, include = c("Bridge Strength")) + 
  theme(axis.text=element_text(size = 6))

print(plot_bridgecen_sg)
```
\newpage

We also assessed the stability of the bridge strength centrality measure using case-drop bootstraps. As depicted in the plot below, the bridge strength centrality estimates were highly stable and accurate.

```{r, results = 'hide'}
# performing case-drop bootstraps for exploratory network
boot_sg <- readRDS("../data/appendix/rds/boot_sg.rds")
#casedropboot <- bootnet(boot_sg, nBoots = 1000, nCores = 8, statistics = "all", communities = communities, type = "case")
#saveRDS(casedropboot, "../data/appendix/rds/casedropboot.rds")
casedropboot <- readRDS("../data/appendix/rds/casedropboot.rds")

# assessing stability of bridge strength using case-drop bootstrap statistics
corStability(casedropboot, statistics = c("bridgeStrength"))
```
```{r}
plot(casedropboot, statistics= c("bridgeStrength"))
```

\newpage

# Appendix 5: Confirmatory Network Analysis for US community Sample

```{r}
set.seed(2022)

# importing clean data for reliability analyses
networkdata_reliability_us <- read.csv("../data/confirmatory/networkdata_reliability_us.csv")

# importing clean data for sample characteristics and network estimation
data_us <- read.csv("../data/confirmatory/networkdata_us.csv")
networkdata_us <- read.csv("../data/confirmatory/networkdata_us.csv") %>% 
  select(-Age)

# importing codebook
variables <- as.data.frame(readxl::read_xlsx("../data/variablebook.xlsx")) %>% 
  select("label", "variablename", "variable_description_short", "variable_description_clean")
```

## Methods

### Participants and Procedure

We used data gathered from a US community sample via Prolific (*n* = 595). After removing duplicate responses and data from participants who had failed attention checks, the final sample size used for the present analysis was 534. Of the 534 participants, 293 participants were male, 236 were female, and 5 preferred not to indicate their gender. Most participants were ethnically Caucasian (69.7%) -- the remaining participants were either African American (15.0%), Hispanic (3.4%), Asian (8.2%), or others/mixed (3.7%). The mean age of this sample was `r mean(data_us$Age, na.rm = TRUE) %>% round(digits = 2)` (*SD* = `r sd(data_us$Age, na.rm = TRUE) %>% round(digits =2)`). Participants were tasked to complete a battery of self-report questionnaires online at their convenience and were reimbursed with cash for their participation.

### Measures

```{r}
#calculating reliability for docs subscales (raw_alpha of output)

#calculating reliability for tpess (raw_alpha of output)
docs_tpess_reli <-networkdata_reliability_us %>%
  select(starts_with("tpess")) %>% 
  psych::alpha()

## docs_con
docs_con_reli <- networkdata_reliability_us %>% 
  select(docs1, docs2, docs3, docs4, docs5) %>% 
  psych::alpha()

## docs_res
docs_res_reli <- networkdata_reliability_us %>% 
  select(docs6, docs7, docs8, docs9, docs10) %>% 
  psych::alpha()

## docs_ut
docs_ut_reli <- networkdata_reliability_us %>% 
  select(docs11, docs12, docs13, docs14, docs15) %>% 
  psych::alpha()

## docs_sym
docs_sym_reli <- networkdata_reliability_us %>% 
  select(docs16, docs17, docs18, docs19, docs20) %>% 
  psych::alpha()
```

The same measures administered to the Singaporean student sample were administered to the US community sample. The internal consistency of the TPESS, DOCS contamination subscale, DOCS responsibility subscale, DOCS unacceptable thoughts subscale, and DOCS symmetry subscale in the US sample was $\alpha$ = `r round(docs_tpess_reli$total$raw_alpha, digits = 2)`, $\alpha$ = `r round(docs_con_reli$total$raw_alpha, digits = 2)`, $\alpha$ = `r round(docs_res_reli$total$raw_alpha, digits = 2)`, $\alpha$ = `r round(docs_ut_reli$total$raw_alpha, digits = 2)`, and $\alpha$ = `r round(docs_sym_reli$total$raw_alpha, digits = 2)` respectively.

### Data Analysis

We estimated a confirmatory network model with the R package *psychonetrics* (version 0.11.5; Epskamp, 2023), fixing the structure of this model to that of the exploratory network detailed in the main paper (indicated by the adjacency matrix, which captures the presence/absence of edges between nodes in the exploratory network) but allowing network parameters to be freely estimated based on the US community sample data. This confirmatory model was based on Spearman correlations with pairwise estimation -- a Spearman correlation matrix (which encoded the Spearman correlations between the same 41 nodes used in the exploratory network model) and average pairwise sample size was used as input. The fit of this confirmatory model was evaluated with the following fit indices [(Schermelleh-Engel et al., 2003)](https://psycnet.apa.org/record/2003-08119-003): root mean square of approximation (RMSEA; $\leq$ 0.05 = good fit, 0.05 to 0.08 = adequate fit, 0.08 to 0.10 = mediocre fit, and > 0.10 = unacceptable), Tucker-Lewis index (TLI), and comparative fit index (CFI; TLI and CFI: > 0.97 = good fit and 0.95 to 0.97 = acceptable fit). The plot of this confirmatory network model was thresholded (using an alpha value of .05), such that only statistically significant edges (*p* < .05) were visually presented. We also imposed the structural layout (i.e. visual position of the nodes within a network) of the exploratory network model onto the confirmatory network model plot, so that the visual position of nodes in both plots were the same.

## Results

```{r, results = 'hide'}
# pulling adjacency matrix from exploratory network
adjmatrix <- as.matrix(read.csv("../data/confirmatory/adjmatrix.csv", row.names = 1))

# obtaining average pairwise sample size for US sample
noNA <- !is.na(networkdata_us)
noNAmat <- t(noNA) %*% noNA
n_pairwise <- mean(noNAmat[lower.tri(noNAmat)])

# fitting confirmatory network model with psychonetrics
# since exploratory model used spearman, should use spearman in confirmatory model for consistency (supply covs and nobs arguments instead of data)
# computationally intensive; code below was saved to a .rds file, to be loaded with readRDS 
cfmnetwork <- ggm(covs = cor(networkdata_us, use = "pairwise.complete.obs", method = "spearman"),
                  nobs = n_pairwise,
                  omega = adjmatrix)
#results_cfmnetwork <- cfmnetwork %>% runmodel()
#saveRDS(results_cfmnetwork, file = "../data/confirmatory/rds/results_cfmnetwork.rds")
results_cfmnetwork <- readRDS(file = "../data/confirmatory/rds/results_cfmnetwork.rds")

# obtaining model fit indices
fit_cfmnetwork <- results_cfmnetwork %>% fit %>% 
  filter(Measure == "df" |Measure == "chisq" | Measure == "rmsea" | Measure == "tli" | Measure == "cfi")
fit_cfmnetwork$Value <- round(fit_cfmnetwork$Value, digits = 2)
```

```{r}
# custom function for defining legend vectors
# DO NOT use if there is only one element
# var_start argument should be argument for dplyr::starts_with
def_legend <- function(data, var_start){
  
  data %>% 
    select(starts_with(var_start)) %>% 
    colnames() %>%  
    match(colnames(data))
}

# defining grouping for legend
group_subscale <- list("GAD" = def_legend(networkdata_us,"gad"),
                       "PHQ-9" = def_legend(networkdata_us,"phq"),
                       "SMPD" = def_legend(networkdata_us,"smpd"),
                       "SMSAD" = def_legend(networkdata_us,"smsp"),
                       "DOCS" = def_legend(networkdata_us,"docs"),
                       "TPESS" = c(which(colnames(networkdata_us) == "tpess")))

# importing nodelabels
nodelabels <- read.csv("../data/nodelabels.csv")

# pulling plot layout of exploratory network
plotlayout <- as.matrix(read.csv("../data/confirmatory/plotlayout.csv"))
```

```{r,fig.height = 30, fig.width = 1.4*30}
#plotting confirmatory network
plot_us <- qgraph(getmatrix(results_cfmnetwork, "omega", threshold = TRUE, alpha = 0.05),
                groups = group_subscale,
                layout = plotlayout,
                cut = 0,
                palette = "pastel",
                vsize = 3,
                labels = nodelabels$label,
                label.cex = 1.5,
                border.width = 0.75,
                legend.cex = 1.42,
                nodeNames = nodelabels$variable_description_short,
                #filename = "cfmnetwork", filetype = "jpeg", width = 20, height = 20,
                theme = "colorblind")
```

The figure above depicts the confirmatory network model fit to data from the US community
sample. The confirmatory model -- $\chi^{2}$(`r (fit_cfmnetwork %>% filter(Measure == "df"))$Value`) = `r (fit_cfmnetwork %>% filter(Measure == "chisq"))$Value`, *p* < .001; RMSEA = `r (fit_cfmnetwork %>% filter(Measure == "rmsea"))$Value`; TLI = `r (fit_cfmnetwork %>% filter(Measure == "tli"))$Value`; CFI = `r (fit_cfmnetwork %>% filter(Measure == "cfi"))$Value` -- fit the data excellently. This indicates that the general network structure of associations between the core vulnerability and internalizing symptoms extracted from the Singaporean student sample in our exploratory analysis was replicated in the US community sample. The symptoms with statistically significant edges with the core vulnerability are presented in the table below. 

The edges between the core vulnerability and three cognition-related symptom nodes -- feeling like a failure, thoughts of rejection, embarrassment, or offending others, and the unacceptable thoughts subscale -- were prominent in the exploratory network and statistically significant in the confirmatory network. As the fit of the confirmatory model is excellent, we may conclude that these edges replicated across our datasets.

```{r, fig.show = 'hide'}
# extracing significance values from CIplot
cfmnetwork_ciplot <- CIplot(results_cfmnetwork, "omega")

significance <- case_when(
  cfmnetwork_ciplot$data$p < 0.0001 ~ "p < .0001",
  cfmnetwork_ciplot$data$p < 0.001 ~ "p < .001",
  cfmnetwork_ciplot$data$p < 0.01 ~ "p < .01",
  cfmnetwork_ciplot$data$p < 0.05 ~ "p < .05",
  cfmnetwork_ciplot$data$p > 0.05 ~ "p > .05"
)

# this chunk of code pulls the edgelist from ci plot and removes absent edges
cfmnetwork_edgelist <- data.frame(edge = as.character(cfmnetwork_ciplot$data$edge),
                                  weight = cfmnetwork_ciplot$data$est,
                                  p = cfmnetwork_ciplot$data$p,
                                  sig = significance) %>%
  filter(edge %in% subset(cfmnetwork_ciplot$data$edge, grepl("tpess", cfmnetwork_ciplot$data$edge, fixed = TRUE))) %>%  #grep1 used to filter for tpess-relevant edges only (returns T/F), subset used to create list of tpess-x edgelist; %in% used to evaluate if edge is in the tpess-x edgelist (returns T/F)
  filter(!is.na(weight) & !is.na(p))

# this chunk of code subsets the edgelist to significant edges only
cfmnetwork_edgelist_sig <- cfmnetwork_edgelist %>%
  filter(sig != "p > .05")

# creating a nice table for significant edges of confirmatory network
cfmnetwork_edgelist_sig$edge <- c("gad2", "gad6", "phq1", "phq6", "smsp3", "docs_ut", "docs_sym")
names(cfmnetwork_edgelist_sig) <- c("variablename", "weight", "p", "sig")
cfmnetwork_edgelist_sig$weight <- round(cfmnetwork_edgelist_sig$weight, digits = 2)
cfmnetwork_edgelist_sig <- left_join(cfmnetwork_edgelist_sig, nodelabels, by = "variablename") %>% 
  select(label, variable_description_short, weight) %>% 
  arrange(desc(weight))
```

\newpage

```{r}
cfmnetwork_edgelist_sig %>%
  kbl(format = "latex", col.names = c("Node Label", "Description", "Edge Weight"), caption = "Confirmatory Network: Weights of Edges between the Core Vulnerability and Internalizing Symptoms", booktabs = TRUE, longtable = TRUE)  %>%
  footnote(
    general_title = "Note.",
    general = "All edges included in this are significant at p < .05. Values in the edge weight column indicate the partial spearman correlation between the core vulnerability node and the corresponding symptom node.",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE)
```

\newpage

# Appendix 6: Factor Score Network
Here we consider a factor score approach: using the factor scores of the core vulnerability and the four DOCS subscales instead of their sum scores to estimate the network we reported in the main manuscript. We report this network here for the interested reader. As detailed below, we decided to retain our use of sum scores for the core vulnerability and the DOCS subscales in our network analysis because the factor score yielded an almost identical network.

The layout of the factor score network was constrained to that of the network reported in the main manuscript (i.e. the original network) for ease of comparison. Factor scores (for both the core vulnerability and the DOCS subscales) were computed using the regression method. Factor scores were highly correlated with the sum scores (~.98 to .99).

```{r, results = 'hide'}
# importing factor scores
tpess_factorscores <- read_sav("../data/fsnetwork/fscores.sav") %>% 
  select(1)
names(tpess_factorscores) <- "tpess_fs"

# importing clean data for network estimation
networkdata_sg_fs <- read.csv("../data/exploratory/networkdata_allitems_sg.csv")

# importing codebook
variables <- as.data.frame(readxl::read_xlsx("../data/variablebook.xlsx")) %>% 
  select("label", "variablename", "variable_description_short", "variable_description_clean")

##################################################################
##          Computing factor scores for DOCS subscales          ##
##################################################################
# subsetting DOCS data
docs_data <- networkdata_sg_fs %>% 
  select(starts_with("docs"))

# specifying and estimating CFA model
docs_structure <-"
docs_con =~ docs1 + docs2 + docs3 + docs4 + docs5
docs_res =~ docs6 + docs7 + docs8 + docs9 + docs10
docs_ut =~ docs11 + docs12 + docs13 + docs14 + docs15
docs_sym =~ docs16 + docs17 + docs18 + docs19 + docs20

# Second-order factor
docs_general =~ docs_con + docs_res + docs_ut + docs_sym
"
docs_model <- cfa(docs_structure, docs_data, missing = "ml")
summary(docs_model, fit.measures = TRUE)

# extracting factor scores
docs_factorscores <- as.data.frame(lavPredict(docs_model, method = "regression")) %>% 
  select(-docs_general)
```

```{r, results = 'hide'}
##################################################################
##                Exploratory network estimation                ##
##################################################################
# merging factor scores with rest of the data
networkdata_sg_fs <- networkdata_sg_fs %>% 
  select(-tpess, -starts_with("docs")) %>% 
  cbind(docs_factorscores) %>% 
  cbind(tpess_factorscores)

# defining node labels for graph
nodelabels <- data.frame(variablename = colnames(networkdata_sg_fs)) %>% 
  left_join(variables, by = "variablename") %>% 
  select(-variable_description_clean)
nodelabels[nodelabels$variablename == "tpess_fs",2] <- "T"
nodelabels[nodelabels$variablename == "tpess_fs",3] <- "TPESS factor score"
nodelabels[nodelabels$variablename == "docs_con",3] <- "Contamination factor score"
nodelabels[nodelabels$variablename == "docs_res",3] <- "Responsibility factor score"
nodelabels[nodelabels$variablename == "docs_ut",3] <- "Unacceptable Thoughts factor score"
nodelabels[nodelabels$variablename == "docs_sym",3] <- "Symmetry factor score"

# estimating network
network_fs <- estimateNetwork(networkdata_sg_fs,
                              default = "EBICglasso",
                              corMethod = "spearman",
                              labels = nodelabels$label,
                              missing = "pairwise",
                              sampleSize = "pairwise_average",
                              tuning = 0.5)

# custom function for defining legend vectors
# DO NOT use if there is only one element
# var_start argument should be argument for dplyr::starts_with
def_legend <- function(data, var_start){
  
  data %>% 
    select(starts_with(var_start)) %>% 
    colnames() %>%  
    match(colnames(data))
}

# defining grouping for legend
group_subscale <- list("GAD" = def_legend(networkdata_sg_fs,"gad"),
                       "PHQ-9" = def_legend(networkdata_sg_fs,"phq"),
                       "SMPD" = def_legend(networkdata_sg_fs,"smpd"),
                       "SMSAD" = def_legend(networkdata_sg_fs,"smsp"),
                       "DOCS" = def_legend(networkdata_sg_fs,"docs"),
                       "TPESS" = c(which(colnames(networkdata_sg_fs) == "tpess_fs")))

# importing plot layout from original exploratory network for ease of comparison
plotlayout <- as.matrix(read.csv("../data/confirmatory/plotlayout.csv"))
```

```{r, fig.height = 30, fig.width = 1.4*30}
# printing plot
plot_fs <- plot(network_fs,
                groups = group_subscale,
                layout = plotlayout, #layout constrained to that of original exploratory network for ease of comparison
                cut = 0,
                palette = "pastel",
                vsize = 3,
                labels = nodelabels$label,
                label.cex = 1.5,
                border.width = 0.75,
                legend.cex = 1.42,
                nodeNames = nodelabels$variable_description_short)

```

\newpage

```{r}
# weight matrices
weightmatrix_main <- as.matrix(read.csv("../data/fsnetwork/weightmatrix.csv"))
weightmatrix_factorscore <- network_fs$graph

#edge weights
edgeweight_main <- weightmatrix_main[lower.tri(weightmatrix_main)]
edgeweight_factorscore <- weightmatrix_factorscore[lower.tri(weightmatrix_factorscore)]

cor_edgeweight <- cor(edgeweight_main, edgeweight_factorscore)
```

To assess how similar this factor score network is to the original network, we computed the correlation between the edge weights of the factor score network and that of the original network.

The edge weights of the factor score network were highly correlated (*r* = `r round(cor_edgeweight, digits = 3)`) with those of the "main" network, indicating that both networks were highly similar. For this reason, we decided to retain our use of sum scores for the core vulnerability and the DOCS subscales in our network analysis.

```{r}
plot(edgeweight_main, edgeweight_factorscore, ylab = "Edge Weights (Factor Score Network)", xlab = "Edge Weights (Original Network)")
```


